The Right Way to Search Evolving Graphs

### 2016-02-20 paper.tex
make figure looks nicer and update caption

\documentclass[10pt,conference,compsocconf]{IEEEtran}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,255,102}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

@@

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.31, line width =1.4pt]
 \node[text width=3cm] at (-9.5, 7.5) {$k=1$};
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

@@

  \foreach \from/\to in {n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
     \draw[dotted,->](n1) -- (n4);
  %\draw[dotted,->](n10) -- (n1);
  %\draw[dotted,->](n4) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
   \begin{tikzpicture}[scale=.31, line width =1.4pt]
 \node[text width=3cm] at (-9.5, 7.5) {$k=2$};
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

@@

  \foreach \from/\to in {n1/n4, n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
    % \draw[dotted,->](n7) to[out=70, in=40] (n11);
  \draw[dotted,->](n4) -- (n12);
  % \draw[dotted,->](n11) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
   \begin{tikzpicture}[scale=.31, line width =1.4pt]
 \node[text width=3cm] at (-9.5, 7.5) {$k=3$};
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

@@

  \foreach \from/\to in {n1/n4, n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
    % \draw[dotted,->](n7) to[out=70, in=40] (n11);
  %\draw[dotted,->](n10) -- (n7);
   %\draw[dotted,->](n11) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{Breadth-first search (BFS) on the evolving graph shown in
Figure~\ref{fig:eg_shortest_path} starting from the root $(1, t_2)$ at iteration
$k = 1, 2, 3$.
Note that the time $t_1$ does not participate in the BFS. Black circles indicate
the active nodes forming the $frontier$ and $nextfrontier$ sets in Algorithm~\ref{alg:bfs},
connected by the dotted black lines.}
\label{fig:example}
\end{figure}

As a simple example, consider the BFS on the example graph in
Figure~\ref{fig:eg_shortest_path} starting from the root $(1, t_2)$.
The procedure is shown in Figure \ref{fig:example}.
The $frontier$ list is first initialized to $\{(1,t_2)\}$.
Since the only forward neighbor of $(1,t_2)$ is $(3,t_2)$,
iteration $k=1$ produces $reached[(3,t_2)]=1$ and $nextfrontier = \{(3,t_2)\}$.
In the next iteration $k=2$, the only forward neighbor of $(3,t_2)$ is $(3,t_3)$,
so $reached[(3,t_3)]=2$ and $nextfrontier = \{(3,t_3)\}$.
The algorithm terminates after $k=3$ after verifying that $(3,t_3)$ has no
forward neighbors.

@@

To study evolving graphs and experiment with various graph types, we have
developed EvolvingGraphs.jl~\cite{zhang15}, a software package for the creation,
manipulation, and study of evolving graphs written in Julia~\cite{bkse12}.
It is freely available online at
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}
\end{center}
and available with the MIT ``Expat'' license. The package contains an implementation
of the evolving graph BFS. \texttt{IntEvolvingGraph}, a data type in EvolvingGraphs.jl,
represents an evolving graph as adjacency lists.
We generate a group of  random (directed) \texttt{IntEvolvingGraph}s with $2000$ nodes and $4$ time stamps, where each edge is included in the graph with
probability $p$.
 Figure \ref{fig:time} shows the plots of  number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted 
in a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with Theorem \ref{thm:complexity}. A summary of the experiments is provided in Table \ref{tab:bfs}.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.png}
  \caption{Experiments of computing Algorithm \ref{alg:bfs} on a group of 
random evolving 
graphs with $2000$ nodes and $4$ time stamps. The x-axis shows the 
number of edges of each evolving graph and the y-axis shows the corresponding
computation time. The values in both axes increase linearly in the direction of 
the arrow.}
  \label{fig:time}
\end{figure}
\begin{table}[h]
\centering
\begin{tabular}{c | c | c | c }
\hline
probability $p$ & no. of edges  & time (s) &  memory (MB) \\\hline
      0.01  &         160,156      & 0.098   & 18.388  \\
      0.09  &       1,440,895        & 0.446  &  134.253  \\
      0.15   &     2,399,774         & 0.743 & 221.511 \\
      0.23   &    3,676,959          & 1.206 &   337.688 \\
      0.31   &     4,956,969          & 1.504  &  494.833 \\
\end{tabular}
\caption{the computation time and the amount of memory allocated for 
computing Algorithm \ref{alg:bfs} on a random evolving graph represented 
adjacency lists with $4$ time stamps and $2000$ nodes.  
Each edge is included in the graph with probability $p$. 
This is a summery of Figure \ref{fig:time}.}
\label{tab:bfs}
\end{table}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.

>>>>

\documentclass[10pt,conference,compsocconf]{IEEEtran}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{lipsum}
\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,255,102}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

@@

 \begin{center}
\begin{figure}[h]
\begin{tcolorbox}[width=3.4in,
                  %%enhanced,
                  %%frame hidden,
                  %interior hidden,
                  boxsep=0pt,
                  left=0pt,
                  right=0pt,
                  top=4pt,
                  ]%%
    \begin{tikzpicture}[scale=.31, line width =1.4pt]
 \node[text width=3cm] at (-9.5, 7.5) {$k=1$};
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

@@

  \foreach \from/\to in {n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
     \draw[dotted,->](n1) -- (n4);
  %\draw[dotted,->](n10) -- (n1);
  %\draw[dotted,->](n4) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{tcolorbox}
\begin{tcolorbox}[width=3.4in,
                  %%enhanced,
                  %%frame hidden,
                  interior hidden,
                  boxsep=0pt,
                  left=0pt,
                  right=0pt,
                  top=4pt,
                  ]%%
   \begin{tikzpicture}[scale=.31, line width =1.4pt]
 \node[text width=3cm] at (-9.5, 7.5) {$k=2$};
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

@@

  \foreach \from/\to in {n1/n4, n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
    % \draw[dotted,->](n7) to[out=70, in=40] (n11);
  \draw[dotted,->](n4) -- (n12);
  % \draw[dotted,->](n11) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{tcolorbox}
\begin{tcolorbox}[width=3.4in,
                  %%enhanced,
                  %%frame hidden,
                  interior hidden,
                  boxsep=0pt,
                  left=0pt,
                  right=0pt,
                  top=4pt,
                  ]%%
   \begin{tikzpicture}[scale=.31, line width =1.4pt]
 \node[text width=3cm] at (-9.5, 7.5) {$k=3$};
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

@@

  \foreach \from/\to in {n1/n4, n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
    % \draw[dotted,->](n7) to[out=70, in=40] (n11);
  %\draw[dotted,->](n10) -- (n7);
   %\draw[dotted,->](n11) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{tcolorbox}
\caption{Breadth-first search (BFS) on the evolving graph shown in
Figure~\ref{fig:eg_shortest_path} starting from the root $(1, t_2)$ at iteration
$k = 1, 2, 3$.
Note that the time $t_1$ does not participate in the BFS. Black circles indicate
the active nodes forming the $frontier$ and $nextfrontier$ sets in Algorithm~\ref{alg:bfs},
connected by the dotted black lines.}
\label{fig:example}
\end{figure}
\end{center}
As a simple example, consider the BFS on the example graph in
Figure~\ref{fig:eg_shortest_path} starting from the root $(1, t_2)$.
The procedure is shown in Figure \ref{fig:example}.
The $frontier$ list is first initialized to $\{(1,t_2)\}$.
Since the only forward neighbor of $(1,t_2)$ is $(3,t_2)$,
iteration $k=1$ produces $reached[(3,t_2)]=1$ and $nextfrontier = \{(3,t_2)\}$.
In the next iteration $k=2$, the only forward neighbor of $(3,t_2)$ is $(3,t_3)$,
so $reached[(3,t_3)]=2$ and $nextfrontier = \{(3,t_3)\}$.
The algorithm terminates after $k=3$ after verifying that $(3,t_3)$ has no
forward neighbors.

@@

To study evolving graphs and experiment with various graph types, we have
developed EvolvingGraphs.jl~\cite{zhang15}, a software package for the creation,
manipulation, and study of evolving graphs written in Julia~\cite{bkse12}.
It is freely available online at
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}
\end{center}
and available with the MIT ``Expat'' license. The package contains an implementation
of the evolving graph BFS. \texttt{IntEvolvingGraph}, a data type in EvolvingGraphs.jl,
represents an evolving graph as adjacency lists.
We generate a group of  random (directed) \texttt{IntEvolvingGraph}s with $2000$ nodes and $4$ time stamps, where each edge is included in the graph with
probability $p$.
 Figure \ref{fig:time} shows the plots of  number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted 
in a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with Theorem \ref{thm:complexity}. A summary of the experiments is provided in Table \ref{tab:bfs}.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.png}
  \caption{Experiments of computing Algorithm \ref{alg:bfs} on a group of 
random evolving 
graphs with $2000$ nodes and $4$ time stamps. The x-axis shows the 
number of edges of each evolving graph and the y-axis shows the corresponding
computation time. The values in the x, y-axis increase linearly from left to 
right and from bottom to top respectively.}
  \label{fig:time}
\end{figure}
\begin{table}[h]
\centering
\begin{tabular}{c | c | c | c }
\hline
probability $p$ & no. of edges  & time (s) &  memory (MB) \\\hline
      0.01  &         160,156      & 0.098   & 18.388  \\
      0.09  &       1,440,895        & 0.446  &  134.253  \\
      0.15   &     2,399,774         & 0.743 & 221.511 \\
      0.23   &    3,676,959          & 1.206 &   337.688 \\
      0.31   &     4,956,969          & 1.504  &  494.833 \\
\end{tabular}
\caption{the computation time and the amount of memory allocated for 
computing Algorithm \ref{alg:bfs} on a random evolving graph represented 
adjacency lists with $4$ time stamps and $2000$ nodes.  
Each edge is included in the graph with probability $p$. 
This is a summery of Figure \ref{fig:time}.}
\label{tab:bfs}
\end{table}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.
